\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[]{hyperref}
\usepackage{fancyhdr}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}


\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
	\vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\newcommand{\resumeItem}[2]{
	\item\small{
		\textbf{#1}{: #2 \vspace{-2pt}}
	}
}

\newcommand{\resumeSubheading}[4]{
	\vspace{-1pt}\item
	\begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
		\textbf{#1} & #2 \\
		\textit{\small#3} & \textit{\small #4} \\
	\end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
	\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
	\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}


\begin{document}

	\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
		\textbf{\Large Masum Billal} & Email : \href{mailto:billalmasum93@gmail.com}{billalmasum93@gmail.com}\\
		\href{https://github.com/proafxin}{\texttt{https://github.com/proafxin}} & Mobile : +8801779788023 \\
	\end{tabular*}


	\section{Education}
	\resumeSubHeadingListStart
	\resumeSubheading
	{University of Dhaka}{Dhaka, Bangladesh}
	{CSE}{$2010-2016$}
	\resumeSubHeadingListEnd

	\section{Experience}
	\resumeSubHeadingListStart

	\resumeSubheading
	{Ixora Solution}{Dhaka, Bangladesh}
	{Sr. Data Scientist and Engineer}{Oct 2020 - Present}
	\resumeItemListStart
	\resumeItem{ShiftSmart Data Pipeline}
	{Currently working to build and deploy a data pipeline for an application called \textit{ShiftSmart}. Technologies: \texttt{GCP, Python, Flask, Docker}, etc.}
	\resumeItem{Paper Search}
	{Currently working as backend developer to build an NLP powered paper searching web application. Technologies: \texttt{Python, Django, Django Rest Framework, Docker}, etc.}
	\resumeItemListEnd

	\resumeSubheading
	{Shohoz}{Dhaka, Bangladesh}
	{Sr. Data Scientist}{Aug 2019 - Nov 2020}
	\resumeItemListStart
	\resumeItem{Corona Tracer BD}
	{Successfully built data pipelines, analytics and visualization and scalable data storage solution for Corona Tracer Bangladesh, a joint venture by Bangladesh government and Shohoz. This project is live at \texttt{http://tracer-admin.ctbd.corona-dghs.xyz/}. Technologies: \texttt{Python, AWS, Boto3, Bokeh, Pandas, Holoviews, Shapely}, etc.}
	\resumeItem{Data pipelines}
	{Built data pipelines for analytics, insights, machine learning services and ETL purposes. Technologies: \texttt{Python, AWS, Boto3, Pandas, PySpark, Azure Service Bus, Azure Event Hub, Apache Kafka}, etc.}
	\resumeItem{Fraud detection}
	{Created automated fraud detection pipelines.}
	\resumeItem{Exploratory analysis}
	{Hands on exploratory data analysis of real user data.}
	\resumeItem{User profiling}
	{Used machine learning to create clusters of users and automated profiling for quest planning.}
	\resumeItem{Data mining, recommendation and others}
	{Developed automated priority dispatching services and used data mining techniques for provider distribution/trend analysis/recommendation.}
	\resumeItemListEnd

	\resumeSubheading
	{Auleek}{Dhaka, Bangladesh}
	{Machine learning engineer}{Sep 2018 - May 2019}
	\resumeSubheading
	{Reve Systems}{Dhaka, Bangladesh}
	{Software engineer, RnD}{Mar 2017 - August 2018}
	\resumeSubHeadingListEnd

	\section{Pet projects}
	\resumeSubHeadingListStart
	\resumeSubItem{Flatten NoSQL}
	{Open source python library for flattening NoSQL-like denormalized data to SQL-like data. Project link: \texttt{https://pypi.org/project/
			flatten-nosql/}}
	\resumeSubItem{Seeding KMeans}
	{My research on k-means clustering. Here I talk about the results in k-means++ paper and discusses various seeding methods of center initialization. Project link: \texttt{https://github.com/proafxin/clustering}}
	\resumeSubItem{Media Recommender System}
	{This is an ongoing project where I tried to generalize different medias (music, game, video, etc) in one place for recommendation. Project link: \texttt{https://github.com/proafxin/media-recommendation}}
	\resumeSubItem{Localizer}
	{In this project, I used \texttt{YOLO} to detect objects in images. Project link: \texttt{https://github.com/proafxin/Localizer}}
	\resumeSubItem{DRF tutorial}
	{I used this project to teach some people at Ixora Solution how \texttt{DRF} (Django Rest Framework) works.}
	\resumeSubHeadingListEnd

	\section{Programming Skills}
	\resumeSubHeadingListStart
	\item{
		\textbf{Languages}{: Python, C, C++, Java}
	}
	\item{
		\textbf{Technologies}{: GCP, Azure, AWS, Git, Pandas, Django, Flask, Django Rest Framework, Flask Restful, SpringBoot, Scikit-learn, Matplotlib, Bokeh, PySpark, PyTorch, Tensorflow, Scipy, Numpy, Kafka, OOP, etc.}
	}
	\resumeSubHeadingListEnd
	\section{Publications}
	\resumeSubHeadingListStart
	\resumeSubItem{Integer Sequences: Divisible, Lucas and Lehmer Sequences}{Masum Billal and Samin Riasat, To be published in Springer Nature soon.}
	\resumeSubItem{Topics in Number Theory: An Olympiad Oriented Approach}{Masum Billal and Amir Hossein, Amazon, ISBN-10: 1719920311.}
	\resumeSubItem{Similarity Aggregation for Collaborative Filtering}{Sheikh
		Muhammad Sarwar, Masum Billal, Mahmudul Hasan, Dimitry I. Ignatov, AIST Conference. \url{http://link.springer.com/chapter/10.1007/978-3-319-26123-2_23}}
	\resumeSubItem{A Nice Theorem in Multiplicative Functions}{Masum Billal, Eureka, The Cambridge University Mathematical Society, Issue 63, 2014}
	\resumeSubItem{Exponent GCD Lemma}{Masum Billal, Mathematical Reflections, Issue 6, 2012}
	\resumeSubItem{10th Bangladesh Mathematical Olympiad: Selected Problems and Solutions}{Bangladesh Math Booklet, 2015. \url{https://karushib.wordpress.com/2016/05/29/bangladesh-booklet-of-math-problems-2015/}}
	\resumeItemListEnd

	\section{Others}
	\resumeSubHeadingListStart
	\resumeSubItem{Mathematics}{Trainer for the International Math Olympiad team, national and extension math camps, 2011-2015.}
	\resumeSubItem{Programming contest}{Rank 9 at the NSU Inter University National Programming Contest, 2013}
	\resumeSubItem{Programming contest}{Rank 13 at the IUT Inter-University Programming Contest, Rank 13}
	\resumeSubItem{Programming contest}{Rank 17 at the ICPC Dhaka Regional, 2013}
	\resumeSubItem{Programming contest}{Rank 18 at the ICPC Dhaka Regional, 2012}
	\resumeSubItem{Mathematics}{Medal at National and Regional Mathematical Olympiads, 2009/10}
	\resumeSubHeadingListEnd
	\section{Interests}
	\resumeSubHeadingListStart
	\item{Mathematics}
	\item{Data science}
	\item{Data engineering}
	\item{Problem solving. Global rank 132 in Hackerrank mathematics section.}
	\item{Gaming. Currently I play Dota 2, Assassin's Creed games, The Witcher 3, etc.}
	\resumeSubHeadingListEnd
\end{document}
